---
title: "Midterm Project: Exploration on Hong Kong People’s Values and Belief"
author: "Shixin Liang"
date: "10/12/2019"
output: pdf_document
---

```{r setup, include=FALSE}
library(psych)
library(GPArotation)
library(tidyverse)
library(readxl)
library(janitor)
library(magrittr)
library(GGally)
library(ggmosaic)

knitr::opts_chunk$set(echo = FALSE)
```
# Introduction
As everyone knows, the 2019 Hong Kong protests lead Hong Kong and China into a severe situation. Clashes between police and activists have become increasingly violent. There are identity problems between protesters and officers. I concern about the situation very much and this project aims to explore Hong Kong people’s values and belief and hope to find out some potential factors that lead to the conflicts.  

# Data Description  
The dataset is World Values Survey data of Hong Kong from 2010 to 2014. The data are results from a survey with 114 questions. Overall, the data collected was based on a scale system. (For example some questions were answered on a 1-10 scale of satisfactory with 1.completely not satisfied and 10.completely satisfied.) The dataset contains 430 total columns and 1000 observations. 

# Data Cleaning  
Prior to any analysis, the data was cleaned by fixing weird value: deleting  columns that only has -2 and -4 value. It is because when a column only has -2 and -4 value it means no one of the 1000 observations answered the question.  
```{r }
# First, we view the data  
Data <- read.csv("Data.csv", header = TRUE)
# Fix weird value: delete -2, -4 columns
Data <- Data[, 1:332]
Data <- Data[, -c(1,2,3,4,46,59,61,129:145,248:281,286,313,315:317,320,322,325,326,330,331)]
Data <- na.omit(Data)
```  
  
   
# Exploratory Factor Analysis  
Since there are 430 variables, it is impossible to analyze all of them. To solve the problem, I did factor analysis. And the result shows that the 430 variables could be classified into 28 categories. 
```{r}
# Parallel Analysis
parallel <- fa.parallel(Data, fm = 'minres', fa = 'fa')
# The plot shows that no more than 28 factors would be good choice.  

# Factor Analysis
# We will select oblique rotation (rotate = “oblimin”) as we believe that there is correlation in the factors. 
get_factor <- fa(Data, nfactors = 28,rotate = "oblimin",fm="minres") 
#print(get_factor)  
#print(get_factor$loadings,cut = 0.1)  

get_factor$rms
get_factor$TLI
get_factor$RMSEA

# plot
#fa.diagram(get_factor) 
```  
   
  
# EDA  
In order to explore Hong Kong people’s values and belief and find out potential factors that lead to the conflicts, there appear to be five main parts for analysis:  
1. Satisfaction with life  
2. Financial situation  
3. Identity  
4. Confidence in the government  
5. Attitude towards democracy  
  
## Satisfaction with life  

### Satisfaction.with.your.life  
```{r}
# make factors
Data$V23..Satisfaction.with.your.life <- as.factor(Data$V23..Satisfaction.with.your.life)
# change levels names -2 into NA
levels(Data$V23..Satisfaction.with.your.life) <- c("NA", 1,2,3,4,5,6,7,8,9,10)

ggplot(Data) +
 aes(x = V23..Satisfaction.with.your.life, fill = V23..Satisfaction.with.your.life) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Satisfaction level", y = "Frequency") + 
  ggtitle("Satisfaction Frequency")+ labs(caption = "Figure 1")

# satisfaction by age
ggplot(Data, mapping = aes(x = V23..Satisfaction.with.your.life, y = V242..Age, fill = V23..Satisfaction.with.your.life)) +
  geom_boxplot(mapping = aes(group = V23..Satisfaction.with.your.life)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Satisfaction level", y = "Age") + 
  ggtitle("Age and Satisfaction level")+ labs(caption = "Figure 2")

```
For Figure 1, 10 means completely satisfied while 1 means completely not satisfied. It shows people are overall satisfied with their life.
  
  
### Feeling.of.happiness
```{r}  
# make factors
Data$V10..Feeling.of.happiness <- as.factor(Data$V10..Feeling.of.happiness)
# change levels names
levels(Data$V10..Feeling.of.happiness) <- c("NA", "very happy", "fairly happy", "not very happy", "completely not happy")

ggplot(Data) +
 aes(x = V10..Feeling.of.happiness, fill = V10..Feeling.of.happiness) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Feeling of Happiness", y = "Frequency") + 
 ggtitle("Feeling of Happiness Frequency")+ labs(caption = "Figure 3")

# Feeling of Happiness by age
ggplot(Data, mapping = aes(x = V10..Feeling.of.happiness, y = V242..Age, fill = V10..Feeling.of.happiness)) +
  geom_boxplot(mapping = aes(group = V10..Feeling.of.happiness)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Feeling of Happiness", y = "Age") + 
  ggtitle("Age and Feeling of Happiness")+ labs(caption = "Figure 4")

```
Figure 3 shows  most people are fairly happy.
  
  
### How.much.freedom.of.choice.and.control.over.own.life
```{r}  
# make factors
Data$V55..How.much.freedom.of.choice.and.control.over.own.life <- as.factor(Data$V55..How.much.freedom.of.choice.and.control.over.own.life)
# change levels names
levels(Data$V55..How.much.freedom.of.choice.and.control.over.own.life) <- c("NA", 1,2,3,4,5,6,7,8,9,10)

ggplot(Data) +
 aes(x = Data$V55..How.much.freedom.of.choice.and.control.over.own.life, fill = Data$V55..How.much.freedom.of.choice.and.control.over.own.life) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Freedom to Choose", y = "Frequency") + 
 ggtitle("Freedom to Choose")+ labs(caption = "Figure 5")

# Freedom to Choos by age
ggplot(Data, mapping = aes(x = V55..How.much.freedom.of.choice.and.control.over.own.life, y = V242..Age, fill = V55..How.much.freedom.of.choice.and.control.over.own.life)) +
  geom_boxplot(mapping = aes(group = V55..How.much.freedom.of.choice.and.control.over.own.life)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Freedom to Choos", y = "Age") + 
  ggtitle("Age and Freedom to Choos")+ labs(caption = "Figure 6")  

```
For Figure 5, 10 means much freedom to choose while 1 means completely no freedom to choose. It shows people are overall satisfied freedom.
  
## Financial situation  
  
### Scale.of.incomes
```{r}
# make factors
Data$V239..Scale.of.incomes <- as.factor(Data$V239..Scale.of.incomes)
# change levels names
levels(Data$V239..Scale.of.incomes) <- c("NA", 1,2,3,4,5,6,7,8,9,10)

ggplot(Data) +
 aes(x = V239..Scale.of.incomes, fill = V239..Scale.of.incomes) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Incomes", y = "Frequency") + 
 ggtitle("Incomes")+ labs(caption = "Figure 7")

# Scale.of.incomes by age
ggplot(Data, mapping = aes(x = V239..Scale.of.incomes, y = V242..Age, fill = V239..Scale.of.incomes)) +
  geom_boxplot(mapping = aes(group = V239..Scale.of.incomes)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Incomes", y = "Age") + 
  ggtitle("Age and Incomes")+ labs(caption = "Figure 8")  

# Mosaic Plots for Satisfaction with life and Incomes
ggplot(Data) +
   geom_mosaic(aes(x = product(V239..Scale.of.incomes, V23..Satisfaction.with.your.life), fill=V239..Scale.of.incomes), na.rm=TRUE) + 
   labs(x = "Income", y = "Satisfaction level", title='Satisfaction with life and Incomes')+ labs(caption = "Figure 9")
```
Figure 5 is in normal distribution form and it is reasonable. Figure 9 is Mosaic Plots for Satisfaction with life and Incomes. It shows people with low income are strongly disatisfied with their life.
  
### Satisfaction.with.financial.situation.of.household
```{r}
# make factors
Data$V59..Satisfaction.with.financial.situation.of.household <- as.factor(Data$V59..Satisfaction.with.financial.situation.of.household)
# change levels names
levels(Data$V59..Satisfaction.with.financial.situation.of.household) <- c("NA", 1,2,3,4,5,6,7,8,9,10)

ggplot(Data) +
 aes(x = V59..Satisfaction.with.financial.situation.of.household, fill = V59..Satisfaction.with.financial.situation.of.household) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Satisfaction with financial situation", y = "Frequency") + 
 ggtitle("Satisfaction with financial situation")+ labs(caption = "Figure 10")

# Satisfaction.with.financial.situation by age
ggplot(Data, mapping = aes(x = V59..Satisfaction.with.financial.situation.of.household, y = V242..Age, fill = V59..Satisfaction.with.financial.situation.of.household)) +
  geom_boxplot(mapping = aes(group = V59..Satisfaction.with.financial.situation.of.household)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Satisfaction with financial situation", y = "Age") + 
  ggtitle("Age and Satisfaction with financial situation")+ labs(caption = "Figure 11")  

```
  
### Are.you.the.chief.wage.earner.in.your.house
```{r}
# make factors
Data$V235..Are.you.the.chief.wage.earner.in.your.house <- as.factor(Data$V235..Are.you.the.chief.wage.earner.in.your.house)
# change levels names
levels(Data$V235..Are.you.the.chief.wage.earner.in.your.house) <- c("NA", "Yes", "No")

ggplot(Data) +
 aes(x = V235..Are.you.the.chief.wage.earner.in.your.house, fill = V235..Are.you.the.chief.wage.earner.in.your.house) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Chief Wage Earner", y = "Frequency") + 
 ggtitle("Chief Wage Earner")+ labs(caption = "Figure 12")

# Chief Wage Earner by age
ggplot(Data, mapping = aes(x = V235..Are.you.the.chief.wage.earner.in.your.house, y = V242..Age, fill = V235..Are.you.the.chief.wage.earner.in.your.house)) +
  geom_boxplot(mapping = aes(group = V235..Are.you.the.chief.wage.earner.in.your.house)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Chief Wage Earner", y = "Age") + 
  ggtitle("Age and Chief Wage Earner")+ labs(caption = "Figure 13")  

```
  
### Is.the.chief.wage.earner.employed.now.or.not
```{r}
# make factors
Data$V236..Is.the.chief.wage.earner.employed.now.or.not <- as.factor(Data$V236..Is.the.chief.wage.earner.employed.now.or.not)
# change levels names
levels(Data$V236..Is.the.chief.wage.earner.employed.now.or.not) <- c("NA", "Yes", "No")

ggplot(Data) +
 aes(x = V236..Is.the.chief.wage.earner.employed.now.or.not, fill = V236..Is.the.chief.wage.earner.employed.now.or.not) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Chief Wage Earner Employment", y = "Frequency") + 
 ggtitle("Chief Wage Earner Employment")+ labs(caption = "Figure 14")

# Chief Wage Earner Employment by age
ggplot(Data, mapping = aes(x = V236..Is.the.chief.wage.earner.employed.now.or.not, y = V242..Age, fill = V236..Is.the.chief.wage.earner.employed.now.or.not)) +
  geom_boxplot(mapping = aes(group = V236..Is.the.chief.wage.earner.employed.now.or.not)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Chief Wage Earner Employment", y = "Age") + 
  ggtitle("Age and Chief Wage Earner Employment")+ labs(caption = "Figure 15")  

```
It is suprisingly that Figure 15 shows older people have higher unemplotment rate.

### Family.savings.during.past.year
```{r}
# make factors
Data$V237..Family.savings.during.past.year <- as.factor(Data$V237..Family.savings.during.past.year)
# change levels names
levels(Data$V237..Family.savings.during.past.year) <- c("NA", "have savings", "make ends meet", "spend some savings", "spend all savings and borrow money")

ggplot(Data) +
 aes(x = V237..Family.savings.during.past.year, fill = V237..Family.savings.during.past.year) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Family Savings", y = "Frequency") + 
 theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8)) +
 ggtitle("Family Savings")+ labs(caption = "Figure 16")

# Family Savings by age
ggplot(Data, mapping = aes(x = V237..Family.savings.during.past.year, y = V242..Age, fill = V237..Family.savings.during.past.year)) +
  geom_boxplot(mapping = aes(group = V237..Family.savings.during.past.year)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Family Savingst", y = "Age") + 
  ggtitle("Age and Family Savings")+ labs(caption = "Figure 17") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8))

```
These plots show that Hong Kong people are overall in good financial situation.
  
## Identity  
  
### How.proud.of.nationality
```{r}
# make factors
Data$V211..How.proud.of.nationality <- as.factor(Data$V211..How.proud.of.nationality)
# change levels names
levels(Data$V211..How.proud.of.nationality) <- c("NA", "very proud", "rather proud", "not very proud", "not proud at all", "I am not a Hong Konger.")

ggplot(Data) +
 aes(x = V211..How.proud.of.nationality, fill = V211..How.proud.of.nationality) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Proud of Nationality", y = "Frequency") + 
 theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8)) +
 ggtitle("Proud of Nationality")+ labs(caption = "Figure 18")

# Proud of Nationality by age
ggplot(Data, mapping = aes(x = V211..How.proud.of.nationality, y = V242..Age, fill = V211..How.proud.of.nationality)) +
  geom_boxplot(mapping = aes(group = V211..How.proud.of.nationality)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Proud of Nationality", y = "Age") + 
  ggtitle("Age and Proud of Nationality")+ labs(caption = "Figure 19") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8))

```
Figure 18 shows people are proud of being a Hong Konger.

### I see myself as a part of the local community, a Hong Konger
```{r}
# make factors
Data$V213..I.see.myself.as.part.of.my.local.community <- as.factor(Data$V213..I.see.myself.as.part.of.my.local.community)
# change levels names
levels(Data$V213..I.see.myself.as.part.of.my.local.community) <- c("NA", "strongly agree", "agree", "disagree", "strongly disagree")

ggplot(Data) +
 aes(x = V213..I.see.myself.as.part.of.my.local.community, fill = V213..I.see.myself.as.part.of.my.local.community) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Identity of Hong Konger", y = "Frequency") + 
 theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8)) +
 ggtitle("Identity of Hong Konger")+ labs(caption = "Figure 20")

# Identity of Hong Konger by age
ggplot(Data, mapping = aes(x = V213..I.see.myself.as.part.of.my.local.community, y = V242..Age, fill = V213..I.see.myself.as.part.of.my.local.community)) +
  geom_boxplot(mapping = aes(group = V213..I.see.myself.as.part.of.my.local.community)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Identity of Hong Konger", y = "Age") + 
  ggtitle("Age and Identity of Hong Konger")+ labs(caption = "Figure 21") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8))

```
  
### I see myself as a part of the Chinese nation
```{r}
# make factors
Data$V214..I.see.myself.as.part.of.the..country..nation <- as.factor(Data$V214..I.see.myself.as.part.of.the..country..nation)
# change levels names
levels(Data$V214..I.see.myself.as.part.of.the..country..nation) <- c("NA", "strongly agree", "agree", "disagree", "strongly disagree")

ggplot(Data) +
 aes(x = V214..I.see.myself.as.part.of.the..country..nation, fill = V214..I.see.myself.as.part.of.the..country..nation) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Identity of part of the Chinese nation", y = "Frequency") + 
 theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8)) +
 ggtitle("Identity of part of the Chinese nation")+ labs(caption = "Figure 22")

# Identity of part of the Chinese nation of Nationality by age
ggplot(Data, mapping = aes(x = V214..I.see.myself.as.part.of.the..country..nation, y = V242..Age, fill = V214..I.see.myself.as.part.of.the..country..nation)) +
  geom_boxplot(mapping = aes(group = V214..I.see.myself.as.part.of.the..country..nation)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Identity of part of the Chinese nation", y = "Age") + 
  ggtitle("Age and Identity of part of the Chinese nation")+ labs(caption = "Figure 23") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8))

```
It is surprisingly that Figure 22 show most people consider themselves as a part of the Chinese nation. And Figure 23 shows that younger people are being less considering themselves as a part of the Chinese nation.
  
## Confidence in the government   
  
### Confidence..The.police
```{r}
# make factors
Data$V113..Confidence..The.police <- as.factor(Data$V113..Confidence..The.police)
# change levels names
levels(Data$V113..Confidence..The.police) <- c("NA", "a lot", "some", "not very much", "none at all")

ggplot(Data) +
 aes(x = V113..Confidence..The.police, fill = V113..Confidence..The.police) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Confidence in the Police", y = "Frequency") + 
 ggtitle("Confidence in the Police")+ labs(caption = "Figure 24")

# Confidence in the Police by age
ggplot(Data, mapping = aes(x = V113..Confidence..The.police, y = V242..Age, fill = V113..Confidence..The.police)) +
  geom_boxplot(mapping = aes(group = V113..Confidence..The.police)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Confidence in the Police", y = "Age") + 
  ggtitle("Age and Confidence in the Police")+ labs(caption = "Figure 25") 

```
Figure 25 shows younger people are significantly have less confidence in the police.

### Confidence..Hong Kong government
```{r}
# make factors
Data$V115..Confidence..The.government..in.your.nation.s.capital. <- as.factor(Data$V115..Confidence..The.government..in.your.nation.s.capital.)
# change levels names
levels(Data$V115..Confidence..The.government..in.your.nation.s.capital.) <- c("NA", "a lot", "some", "not very much", "none at all")

ggplot(Data) +
 aes(x = V115..Confidence..The.government..in.your.nation.s.capital., fill = V115..Confidence..The.government..in.your.nation.s.capital.) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Confidence in Hong Kong government", y = "Frequency") + 
 ggtitle("Confidence in Hong Kong government")+ labs(caption = "Figure 26")

# Confidence in Hong Kong government by age
ggplot(Data, mapping = aes(x = V115..Confidence..The.government..in.your.nation.s.capital., y = V242..Age, fill = V115..Confidence..The.government..in.your.nation.s.capital.)) +
  geom_boxplot(mapping = aes(group = V115..Confidence..The.government..in.your.nation.s.capital.)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Confidence in Hong Kong government", y = "Age") + 
  ggtitle("Age and Confidence in Hong Kong government")+ labs(caption = "Figure 27") 

```
Figure 27 shows younger people are significantly have less confidence in Hong Kong government.
  
### Confidence..Mainland government
```{r}
# make factors
Data$V125_17..Confidence..Mainland.government <- as.factor(Data$V125_17..Confidence..Mainland.government)
# change levels names
levels(Data$V125_17..Confidence..Mainland.government) <- c("NA", "a lot", "some", "not very much", "none at all")

ggplot(Data) +
 aes(x = V125_17..Confidence..Mainland.government, fill = V125_17..Confidence..Mainland.government) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Confidence in Mainland government", y = "Frequency") +
 ggtitle("Confidence in Mainland government")+ labs(caption = "Figure 28")

# Confidence in Mainland government by age
ggplot(Data, mapping = aes(x = V125_17..Confidence..Mainland.government, y = V242..Age, fill = V125_17..Confidence..Mainland.government)) +
  geom_boxplot(mapping = aes(group = V125_17..Confidence..Mainland.government)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Confidence in Mainland government", y = "Age") + 
  ggtitle("Age and Confidence in Mainland government")+ labs(caption = "Figure 29") 

```
Sadly, Figure 28 shows most people have no confidence in Mainland government.
Figure 29 shows younger people are significantly have less confidence in Mainland government.

  
## Attitude towards democracy  
  
### Importance.of.democracy
```{r}
# make factors
Data$V140..Importance.of.democracy <- as.factor(Data$V140..Importance.of.democracy)
# change levels names
levels(Data$V140..Importance.of.democracy) <- c("NA", 1,2,3,4,5,6,7,8,9,10)

ggplot(Data) +
 aes(x = V140..Importance.of.democracy, fill = V140..Importance.of.democracy) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Importance of Democracy", y = "Frequency") +
 ggtitle("Importance of Democracy")+ labs(caption = "Figure 30")

# Importance of Democracy by age
ggplot(Data, mapping = aes(x = V140..Importance.of.democracy, y = V242..Age, fill = V140..Importance.of.democracy)) +
  geom_boxplot(mapping = aes(group = V140..Importance.of.democracy)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Importance of Democracy", y = "Age") + 
  ggtitle("Age and Importance of Democracyt")+ labs(caption = "Figure 31") 

```
For Figure 30, 10 means very important while 1 means not very important. It shows people are overall consider democracy important.
  
### How.democratically.is.this.country.being.governed.today
```{r}
# make factors
Data$V141..How.democratically.is.this.country.being.governed.today <- as.factor(Data$V141..How.democratically.is.this.country.being.governed.today)
# change levels names
levels(Data$V141..How.democratically.is.this.country.being.governed.today) <- c("NA", 1,2,3,4,5,6,7,8,9,10)

ggplot(Data) +
 aes(x = V141..How.democratically.is.this.country.being.governed.today, fill = V141..How.democratically.is.this.country.being.governed.today) +
 geom_bar() +
 scale_fill_viridis_d(option = "viridis") + 
 theme_minimal()+labs(x = "Today's Democracy Level", y = "Frequency") +
 ggtitle("Today's Democracy Level")+ labs(caption = "Figure 32")

# Today's Democracy Leve by age
ggplot(Data, mapping = aes(x = V141..How.democratically.is.this.country.being.governed.today, y = V242..Age, fill = V141..How.democratically.is.this.country.being.governed.today)) +
  geom_boxplot(mapping = aes(group = V141..How.democratically.is.this.country.being.governed.today)) +
  scale_fill_viridis_d(option = "viridis") + 
  theme_minimal()+labs(x = "Today's Democracy Level", y = "Age") + 
  ggtitle("Age and Today's Democracy Level")+ labs(caption = "Figure 33") 

```
For Figure 33, 10 means very democratic while 1 means not democratic at all. It shows younger people think the society is more democratic.  
